Metadata control document

### 2023-05-25 metadata/metadata_control.Rmd
Switching over to MS cruise instead of MC and MT separately

```{r Interpolate to sample sites}
interp_df <- lst(complete_file_data, complete_env_data) %>%
  bind_rows(.id = "data_type") %>%
  mutate(station_grouping=case_when(
    station%in%as.character(74:86)~"falkor_anticyc",
    station%in%as.character(28:70)~"falkor_cyc",
    TRUE~station
  )) %>%
  split(.$station_grouping) %>%
  map(function(single_station){
    single_station %>%
      mutate(across(c(lat:beam_atten), function(col){
        if(all(is.na(col)))return(NA)
        approx(abs_depth, col, xout = abs_depth, rule = 2, ties = mean)$y
        # pmax(0, predict(loess(col~abs_depth, data = ., span = 1), newdata = .))
      }))
  }) %>%
  bind_rows() %>%
  filter(data_type=="complete_file_data") %>%
  select(-data_type, -time) %>%
  left_join(complete_env_data %>% distinct(station, cast, time), by=c("station", "cast"))
# Correct wonky PC values (those greater than 4) with a linear model built on beam_atten
interp_df <- interp_df %>%
  mutate(pred_PC=interp_df %>% 
           filter(PC_um<4) %>%
           lm(formula=PC_um~beam_atten) %>%
           predict(newdata=interp_df)) %>%
  mutate(PC_um=ifelse(PC_um>4, pred_PC, PC_um)) %>%
  select(-pred_PC) %>%
# Discretize SLA and time
  mutate(sla_class=case_when(
    sla_corr < -5 ~ "Cyclone",
    sla_corr > 5 ~ "Anticyclone",
    TRUE ~ "Neither"
  )) %>%
  mutate(time=as.POSIXct(time, origin="1970-01-01")) %>%
  mutate(time_class=c("Night", "Morning", "Midday", "Evening")[
    floor((as.numeric(format(time, "%H"))+3)/6)%%4+1
  ]) %>%
  bind_rows(extra_filedata)
write_csv(interp_df, "filled_file_metadata.csv")
```

>>>>

```{r Interpolate to sample sites}
interp_df <- lst(complete_file_data, complete_env_data) %>%
  bind_rows(.id = "data_type") %>%
  mutate(station_grouping=case_when(
    station%in%as.character(74:86)~"falkor_anticyc",
    station%in%as.character(28:70)~"falkor_cyc",
    TRUE~station
  )) %>%
  split(.$station_grouping) %>%
  map(function(single_station){
    single_station %>%
      mutate(across(c(lat:beam_atten), function(col){
        if(all(is.na(col)))return(NA)
        approx(abs_depth, col, xout = abs_depth, rule = 2, ties = mean)$y
        # pmax(0, predict(loess(col~abs_depth, data = ., span = 1), newdata = .))
      }))
  }) %>%
  bind_rows() %>%
  filter(data_type=="complete_file_data") %>%
  select(-data_type, -time) %>%
  left_join(complete_env_data %>% distinct(station, cast, time), by=c("station", "cast"))
# Correct wonky PC values (those greater than 4) with a linear model built on beam_atten
interp_df <- interp_df %>%
  mutate(pred_PC=interp_df %>% 
           filter(PC_um<4) %>%
           lm(formula=PC_um~beam_atten) %>%
           predict(newdata=interp_df)) %>%
  mutate(PC_um=ifelse(PC_um>4, pred_PC, PC_um)) %>%
  select(-pred_PC) %>%
# Discretize SLA and time
  mutate(sla_class=case_when(
    sla_corr < -5 ~ "Cyclone",
    sla_corr > 5 ~ "Anticyclone",
    TRUE ~ "Neither"
  )) %>%
  mutate(time=as.POSIXct(time, origin="1970-01-01")) %>%
  mutate(time_class=c("Night", "Morning", "Midday", "Evening")[
    floor((as.numeric(format(time, "%H"))+3)/6)%%4+1
  ]) %>%
  bind_rows(extra_filedata) %>%
  mutate(cruise=ifelse(cruise%in%c("MC", "MT"), "MS", cruise))
write_csv(interp_df, "filled_file_metadata.csv")
```
